Self Referencing Sequences

### 2014-11-07 draft.tex
Edits to Iterative Process

Before we do so however we will clarify two different notions of convergence, that will allow us to state our result more precisely. 
\begin{definition} We say that a sequence $s^{(i)}$ is weakly convergent to $s(C,a)$ if $s^{\infty}$ exists and $s^{\infty} = s(C,a)$. We say that the sequence $s^{(i)}$ is strongly convergent to $s(C,a)$ if $s^{(i)}$ is a prefix of $s(C,a)$ for all $i \geq k$ for some $k\geq 0$. 
\end{definition}
Note that all strongly convergent sequences are also weakly convergent.

\begin{theorem}
Let $C$ be some generating cycle. Let $s^0 = a$ for some $a \in C$ where $a \neq 1$, and let $s^{(i)}$ be the sequences generated by the iterative process. Then $s^{(i})$ is strongly convergent to $s(C,a)$.
\end{theorem}

@@

For the inductive step, we observe that a prefix of the sequence describes the block lengths of a \emph{longer} prefix of the sequence. We know that the sequence it describes is longer because the length of $s^{(i+1)}$ equals the sum of of the numbers in $s^{(i)}$, which is strictly greater than the length of $s^{(i)}$ (since there are numbers that are greater than 1).

@@

Since very $s^{(i)}$ is a prefix of $s(C,a)$, we know that once $s^{(i)}_{j}$ has been assigned a value, $s^{(k)}_{j}$ will have the same value for all $k \geq i$. Because of this $\lim_{i\rightarrow \infty} s^{(i)}_{j}$ is well defined and so $s^{\infty}$ exists. As the limit of the process we know that $s^{\infty}$ is a prefix of $s(C,a)$, but since at every step of the process the length of the sequence strictly increases we must have that $s^{\infty}$ has infinite length, and so $s^{\infty} = s(C,a)$.

\end{proof}

@@

Above we only considered starting sequences which have length one,  but we can be less restrictive about what our starting sequence, $s^{(0)}$, is. Going back to the case of $C = (1 2)$, we can let $s^{(0)}$ be \emph{any} sequence of 1's and 2's that starts with a 2 and the limiting sequence will still be the self-referential sequence.
For example, suppose $s^{(0)} = 2,1,1,1,2$. The rules for generating $s^{(i)}$ give:
\begin{align*}
s^{(0)}&= \mathbf{2},1,1,1,2\\
s^{(1)} &= \mathbf{2,2,1},2,1,2,2\\
s^{(2)} &= \mathbf{2,2,1,1,2,1},1,2,1,1,2,2\\
s^{(3)} &= \mathbf{2,2,1,1,2,1,2,2,1,2},1,1,2,1,2,2,1,1\\
&\vdots
\end{align*}
Here, we bold the numbers that form a prefix of $s(C,2)$. We note that $s^\infty = s(C,a)$ because because $s^{(0)}$ contains a 2 at the beginning, which by the above theorem will produce $s(C,a)$ in the limit. This is true in general.

\begin{corollary}
Let $C$ be some generating cycle, let $s^(0)$ be any sequence of elements of $C$ which begins with some $a \in C$ such that $a \neq 1$. Then $s^{(i)}$ is weakly convergent to $s(C,a)$. 
\end{corollary}
\begin{proof} 
\end{proof}

It is unclear what conditions must be placed on the starting sequence in order to ensure strong convergence, although based on numerical simulation we suspect that applying the process to the starting sequence $2222$ 
%
%\begin{conj} Let $C = (1,2)$. A sequence $s^{(i)}$ is weakly convergent but not strongly convergent to $s(C, a)$ if the starting sequence begins with an $a \in \{1,2\}$ and contains 4 or more elements.
%\end{conj} 
%We make this conjecture on the basis on computer simulations which executes the iterative process to at least 20 iterations. More iterations were not completed because after this point the simulations began to take impractically long amounts of time to complete.

>>>>

Before we do so however we will clarify two different notions of convergence, that will allow us to state our result more precisely. 
\begin{definition} We say that a sequence $s^{(i)}$ is weakly convergent to $s(C,a)$ if $s^{\infty}$ exists and $s^{\infty} = s(C,a)$. We say that the sequence $s^{(i)}$ is strongly convergent to $s(C,a)$ if $s^{(i)}$ is a prefix of $s(C,a)$ for all $i \geq k$ for some $k\geq 0$. 
\end{definition}
Note that all strongly convergent sequences are also weakly convergent. We now can show that if we specify a generating cycle any one element starting sequence (other than $1$) is strongly convergent to the self referencing sequence that begins with the element.

\begin{theorem}
\label{iteratetheorem}
Let $C$ be some generating cycle. Let $s^{(0)} = a$ for some $a \in C$ where $a \neq 1$, and let $s^{(i)}$ be the sequences generated by the iterative process. Then $s^{(i)}$ is strongly convergent to $s(C,a)$.
\end{theorem}

@@

For the inductive step, we observe that a prefix of the sequence describes the block lengths of a \emph{longer} prefix of the sequence. We know that the sequence it describes is longer because the length of $s^{(i+1)}$ equals the sum of of the numbers in $s^{(i)}$, which is strictly greater than the length of $s^{(i)}$.

@@

Since very $s^{(i)}$ is a prefix of $s(C,a)$, we know that once $s^{(i)}_{j}$ has been assigned a value, $s^{(k)}_{j}$ will have the same value for all $k \geq i$. Because of this the limit is well defined and so $s^{\infty}$ exists. As the limit of the process we know that $s^{\infty}$ is a prefix of $s(C,a)$, but since at every step of the process the length of the sequence strictly increases we must have that $s^{\infty}$ has infinite length, and so $s^{\infty} = s(C,a)$. 
\end{proof}

@@

Above we only considered starting sequences which have length one,  but we would like to consider arbitrary starting sequences. Going back to the case of $C = (1 2)$, we can let $s^{(0)}$ be \emph{any} sequence of 1's and 2's that starts with a 2 and the limiting sequence will still be the self-referential sequence.
For example, suppose $s^{(0)} = 2,1,1,1,2$. The rules for generating $s^{(i)}$ give:
\begin{align*}
s^{(0)}&= \mathbf{2},1,1,1,2\\
s^{(1)} &= \mathbf{2,2,1},2,1,2,2\\
s^{(2)} &= \mathbf{2,2,1,1,2,1},1,2,1,1,2,2\\
s^{(3)} &= \mathbf{2,2,1,1,2,1,2,2,1,2},1,1,2,1,2,2,1,1\\
&\vdots
\end{align*}
Here, we bold the numbers that form a prefix of $s(C,2)$. We note that $s^\infty = s(C,a)$ because $s^{(0)}$ contains a 2 at the beginning, which by the above theorem will produce $s(C,a)$ in the limit. This is true in general.

\begin{corollary}
Let $C$ be some generating cycle, let $s^{(0)}$ be any sequence of elements of $C$ which begins with some $a \in C$ such that $a \neq 1$. Then $s^{(i)}$ is weakly convergent to $s(C,a)$. 
\end{corollary}
\begin{proof} 
This follows directly from Theorem \ref{iteratetheorem}. That is because $s^{(0)}$ begins with an $a$, at each step of the process $s^{(i)}$ will be a prefix of $s(C,a)$ followed by some terms that disagree with $s(C,a)$. In the limit the prefix of $s(C,a)$ becomes $s(C,a)$ and so $s^{\infty} = s(C,a)$.
\end{proof}
Note that we do not guarantee strong convergence as there are some starting sequences, such as $2222$ which in numerical simulation appears to produce sequences which disagree with the $s( (12), 2)$ on a constant fraction of indices. We would like to be able to produce a general result that distinguishes between strongly and weekly convergent subsequences but it is unclear that there is a nice categorization of them.

%
%\begin{conj} Let $C = (1,2)$. A sequence $s^{(i)}$ is weakly convergent but not strongly convergent to $s(C, a)$ if the starting sequence begins with an $a \in \{1,2\}$ and contains 4 or more elements.
%\end{conj} 
%We make this conjecture on the basis on computer simulations which executes the iterative process to at least 20 iterations. More iterations were not completed because after this point the simulations began to take impractically long amounts of time to complete.
